---
title: "Stock Analysis"
output: html_document
date: "2024-09-18"
always_allow_html: true
---

Load necessary packages
```{r setup, include=FALSE, message=FALSE}

# Install all necessary packages
#install.packages(c(
#  "rvest", 
# "dplyr", 
# "tidyr", 
# "quantmod", 
#  "ggplot2", 
#  "scales", 
#  "shiny", 
#  "shinydashboard"
#))

library(rvest)
library(dplyr)
library(tidyr)
library(quantmod)
library(ggplot2)
library(scales)
library(shiny)
library(shinydashboard)

#Consider Amazon index
ticker <- "AMZN"

```


Fetch the S&P 500 company list from Wikipedia
```{r}
sp500_url <- "https://en.wikipedia.org/wiki/List_of_S%26P_500_companies"

sp500 <- read_html(sp500_url) %>%
  html_node("table") %>%
  html_table()
```


Clean up the columns
```{r}
sp500 <- sp500 %>%
  select(Symbol, Security, `GICS Sector`, `GICS Sub-Industry`, `Headquarters Location`)
names(sp500) <- c("Ticker", "Name", "Sector", "Industry", "HQ_Location")
```


Initialize a empty dataframe to store stock prices
```{r}
returns <- data.frame(Date = as.Date(character()), 
                      Open = numeric(), 
                      High = numeric(), 
                      Low = numeric(), 
                      Close = numeric(), 
                      Adj_Close = numeric(), 
                      Volume = numeric(), 
                      Ticker = character(), 
                      stringsAsFactors = FALSE)
```


Loop through each sticker of sp500
```{r, error=FALSE, eval=FALSE}
for (symbol in sp500$Ticker) {
  print(symbol)  # Print each symbol to track progress
  
  # Try downloading the stock data using getSymbols
  stock_data <- tryCatch({
    getSymbols(symbol, 
               from = "2010-09-09", 
               to = "2024-09-09", 
               auto.assign = FALSE)
  }, error = function(e) {
    message(paste("Error fetching data for", symbol, ":", e$message))
    return(NULL)  # Return NULL when an error occurs
  })
  
  # Check if stock_data is not NULL (i.e., no error occurred)
  if (!is.null(stock_data)) {
    # Convert the xts object to a data frame for easier manipulation
    stock_df <- data.frame(Date = index(stock_data), coredata(stock_data))
    
    # Rename columns to match your 'returns' data frame
    colnames(stock_df) <- c("Date", "Open", "High", "Low", "Close", "Volume", "Adj_Close")
    
    # Add the ticker symbol to each row
    stock_df$Ticker <- symbol
    
    # Bind the stock data to the 'returns' data frame
    returns <- rbind(returns, stock_df)
  }
}

```


Adjust returns table
```{r}
names(returns) <- c("Date", "Open", "High", "Low", "Close", "Adj_Close", "Volume", "Ticker")

returns <- returns %>% select("Date", "Ticker", "Open", "High", "Low", "Close")

returns <- returns %>% mutate(
  Open = as.numeric(Open),
  High = as.numeric(High),
  Low = as.numeric(Low),
  Close = as.numeric(Close)
)

returns <- returns %>% mutate(
  Movement = ifelse(Close > Open, "Up", "Down")
)
```


Create returns_long table and merge 
```{r}
return_long <- returns %>% gather("Series", "Value", -Date, -Ticker, -Movement)
return_long <- return_long %>% left_join(sp500 %>% select(Ticker, Name, Sector, Industry), by = c("Ticker" = "Ticker"))
```


Creation of a candlestick 
```{r}

# Example charting data (replace with your actual data)
charting_data <- return_long %>% 
  filter(Ticker == ticker, Date >= "2024-08-10")

# Ensure Date is a factor to plot boxplots
charting_data$Date <- as.factor(charting_data$Date)

# Create the boxplot
candlestick <- ggplot(charting_data) +
  geom_boxplot(aes(x = Date, y = Value, fill = Movement), color = "#D0D3D4", width = 0.2) +
  scale_fill_manual(values = c(Up = "#0066ff", Down = "#ffff00")) + 
  xlab("Date") + 
  ylab("Stock Price") +
  labs(
    title = paste0(charting_data$Name[1], "(",ticker,")"),
    subtitle = charting_data$Sector[1]
  ) +
  scale_y_continuous(label = scales::dollar) + 
  theme(
    plot.background = element_rect(fill = "#17202A"),
    panel.background = element_rect(fill = "#17202A"),
    axis.text.x = element_blank(),  # Hides the dates on the x-axis
    axis.text.y = element_text(color = "#ffffff"),
    axis.title.x = element_text(color = "#ffffff"),
    axis.title.y = element_text(color = "#ffffff"),
    plot.title = element_text(color = "#ffffff"),
    plot.subtitle = element_text(color = "#ffffff"),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(color = "#273746"),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    legend.position = "none"
  )

candlestick
```

Calculate long-term performance values
```{r,eval=FALSE}
#Creating a matrix 
performance_summary <- as.data.frame(matrix(NA,ncol = 7, nrow = 0))
names(performance_summary) <- c("Ticker", "Thirty_days", "Ninety_days", "One_year", "Three_years", "Five_years", "Ten_years")


i <- 1
for (ticker in unique(return_long$Ticker)) {
  print(ticker)
  
  return_long_by_ticker <- return_long %>% filter(Ticker == ticker, Series == "Close") %>% arrange(desc(Date))
  
  thirty_days <- (return_long_by_ticker$Value[1] - return_long_by_ticker$Value[21])/return_long_by_ticker$Value[21]
  ninety_days <- (return_long_by_ticker$Value[1] - return_long_by_ticker$Value[63])/return_long_by_ticker$Value[63]
  one_year <- (return_long_by_ticker$Value[1] - return_long_by_ticker$Value[253])/return_long_by_ticker$Value[253]
  three_years <- (1 + ((return_long_by_ticker$Value[1] - return_long_by_ticker$Value[759])/return_long_by_ticker$Value[759]))^(1/3)-1
  five_years <- (1 + ((return_long_by_ticker$Value[1] - return_long_by_ticker$Value[1265])/return_long_by_ticker$Value[1265]))^(1/5)-1
  ten_years <- (1 + ((return_long_by_ticker$Value[1] - return_long_by_ticker$Value[2518])/return_long_by_ticker$Value[2518]))^(1/10)-1
  
  performance_summary[i,1] <- ticker
  performance_summary[i,2] <- thirty_days
  performance_summary[i,3] <- ninety_days
  performance_summary[i,4] <- one_year
  performance_summary[i,5] <- three_years
  performance_summary[i,6] <- five_years
  performance_summary[i,7] <- ten_years


  
  i <- i + 1
}

performance_summary <- performance_summary %>% left_join(sp500, by = c("Ticker" = "Ticker"))
```

Create graphs for the long term performances 

- Price chart
```{r}

price_data <- return_long %>% 
  filter(Ticker == ticker, Series == "Close")

# Create a linechart
price_chart <- ggplot(price_data) +
  geom_line(aes(x = Date, y = Value), color = "#0066ff") +
  xlab("Date") + 
  ylab("Stock Price") +
  labs(
    title = paste0(price_data$Name[1], "(",ticker,")"),
    subtitle = price_data$Sector[1]
  ) +
  scale_y_continuous(label = scales::dollar) + 
  theme(
    plot.background = element_rect(fill = "#17202A"),
    panel.background = element_rect(fill = "#17202A"),
    axis.text.x = element_text(color = "#ffffff"),
    axis.text.y = element_text(color = "#ffffff"),
    axis.title.x = element_text(color = "#ffffff"),
    axis.title.y = element_text(color = "#ffffff"),
    plot.title = element_text(color = "#ffffff"),
    plot.subtitle = element_text(color = "#ffffff"),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(color = "#273746"),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    legend.position = "none"
  )

price_chart
```

-Industry Chart
```{r, warning=FALSE}
sector <- sp500 %>% filter(Ticker == ticker) %>% select(Sector) %>% as.character()
industry <- sp500 %>% filter(Ticker == ticker) %>% select(Industry) %>% as.character()

industry_summary_charting <- performance_summary %>% filter(Sector == sector) %>% mutate(isIndustry = ifelse(Industry == industry, "Industry", "Non_Industry"))

# Create the barplot
industry_chart <- ggplot(industry_summary_charting) +
  geom_bar(aes(x = Industry, y = One_year, fill = isIndustry), stat = "summary", fun= "mean") +
  scale_fill_manual(values = c(Industry = "#ffff00", Non_Industry = "#0066ff")) + 
  ylab("One Year Return") +
  labs(
    title = "Industry Returns"
  ) +
  scale_y_continuous(label = scales::percent) + 
  theme(
    plot.background = element_rect(fill = "#17202A"),
    panel.background = element_rect(fill = "#17202A"),
    axis.text.x = element_text(color = "#ffffff"),
    axis.text.y = element_text(color = "#ffffff"),
    axis.title.x = element_text(color = "#ffffff"),
    axis.title.y = element_text(color = "#ffffff"),
    plot.title = element_text(color = "#ffffff"),
    plot.subtitle = element_text(color = "#ffffff"),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(color = "#273746"),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    legend.position = "none"
  ) +
  coord_flip()

industry_chart

```

- Performance Chart
```{r}
preformance_summary_data <- performance_summary %>% 
  filter(Ticker == ticker) %>%
  select(Thirty_days, Ninety_days, One_year, Three_years, Five_years, Ten_years)

preformance_summary_data <- preformance_summary_data %>% gather("Period", "Return")

preformance_summary_data <- preformance_summary_data %>% mutate(
  Period = case_when(
    Period == "Thirty_days" ~ "1 Month",
    Period == "Ninety_days" ~ "1 Quarter",
    Period == "One_year" ~ "1 Year",
    Period == "Three_years" ~ "3 Years",
    Period == "Five_years" ~ "5 Years",
    Period == "Ten_years" ~ "10 Years",
  )
)

preformance_summary_data$Period <- factor(preformance_summary_data$Period, levels = c("1 Month", "1 Quarter", "1 Year", "3 Years", "5 Years", "10 Years" ))

# Create the barplot
performance_chart <- ggplot(preformance_summary_data) +
  geom_bar(aes(x = Period, y = Return), stat = "identity",fill = "#0066ff") +
  ylab("Annualized Return") +
  labs(
    title = "Returns"
  ) +
  scale_y_continuous(label = scales::percent) + 
  theme(
    plot.background = element_rect(fill = "#17202A"),
    panel.background = element_rect(fill = "#17202A"),
    axis.text.x = element_text(color = "#ffffff"),
    axis.text.y = element_text(color = "#ffffff"),
    axis.title.x = element_text(color = "#ffffff"),
    axis.title.y = element_text(color = "#ffffff"),
    plot.title = element_text(color = "#ffffff"),
    plot.subtitle = element_text(color = "#ffffff"),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(color = "#273746"),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    legend.position = "none"
  )

performance_chart
```




